---
title: "Node_creator_3category"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
```


## file details:
###  (1) Filter Authors after 1960 , remove authors witout CIP, remove authors without region
#### (2) join CIP Category
#### (3) create 5 yearly columns from 1999 to 2018
#### (4) separate authors based on Region
#### (5) Save files




#### Read Files
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author = read.csv('Data/brain_author.csv', stringsAsFactors = FALSE)
df_cip_cat = read.csv('Data/unique_CIP_list_3category.csv', stringsAsFactors = FALSE)
df_author
df_cip_cat
```
### Filter Authors after 1960 , remove authors witout CIP, remove authors without region
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author = df_author %>% filter(min_pub_year > 1960) %>% filter(!is.na(cip_title)) %>% filter(!is.na(region))
df_author
print("------------ After Removing authors without CIP TITLE and first_publication after 1960 -------------")
print(paste0('Total Authors         : ',nrow(df_author)))

```
#### join CIP Category
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author$scopus_id = as.factor(df_author$scopus_id)
df_author$cip_title = as.factor(df_author$cip_title)

colnames(df_cip_cat) <- c('cip_title', 'cip_type', 'combined_cip')
df_cip_cat$cip_title = as.factor(df_cip_cat$cip_title)
df_cip_cat$cip_type = as.factor(df_cip_cat$cip_type)

df_author = df_author %>% merge(df_cip_cat, by='cip_title')
df_author
```


#### create 5 yearly columns from 1999 to 2018
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author = df_author %>% mutate(y_1999 = ifelse(min_pub_year <= 2003, 1, 0))
df_author = df_author %>% mutate(y_2004 = ifelse(min_pub_year <= 2008, 1, 0))
df_author = df_author %>% mutate(y_2009 = ifelse(min_pub_year <= 2013, 1, 0))
df_author = df_author %>% mutate(y_2014 = ifelse(min_pub_year <= 2018, 1, 0))
df_author

```

#### separate authors based on REGION
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author_us = df_author %>% filter(region == 'US/Canada')
df_author_eu = df_author %>% filter(region == 'Europe')
df_author_australasia = df_author %>% filter(region == 'Australasia')

df_author_us
df_author_eu
df_author_australasia
```

#### select spefic columns
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_author_us = df_author_us %>% select(scopus_id, firstName, lastName, school, cip_title, cip_type, country, region, h_index, num_publications, citations, 
                                       min_pub_year, y_05, y_1999, y_2004, y_2009, y_2014)
df_author_eu = df_author_eu %>% select(scopus_id, firstName, lastName, school, cip_title, cip_type, country, region, h_index, num_publications, citations, 
                                       min_pub_year, y_05, y_1999, y_2004, y_2009, y_2014)
df_author_australasia = df_author_australasia %>% select(scopus_id, firstName, lastName, school, cip_title, cip_type, country, region, h_index, num_publications, 
                                                         citations, min_pub_year, y_05, y_1999, y_2004, y_2009, y_2014)
```



#### Save as Node file
```{r echo=FALSE, warning=FALSE, message=FALSE}
write.csv(df_author_us, 'Data/Node_US_3cat.csv')
write.csv(df_author_eu, 'Data/Node_Europe_3cat.csv')
write.csv(df_author_australasia, 'Data/Node_Australasia_3cat.csv')
```





