---
title: "Panel_modeling_article_level"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(rcompanion)
library(rms)
# library(miceadds)
# library(foreign)
# library(haven)
# library(pglm)
# library(sandwich)
# library(lmtest)
# library(clubSandwich)
# library(clusterSEs)
# library(MASS)
# library(questionr)
# library(stargazer)
```



#### Input File Location
```{r echo=FALSE, warning=FALSE, message=FALSE}
# article_file = 'Data/ArticleLevel-RegData-ALLSA_Xc_1_NData_655386_LONGXCIP2.csv'
article_file = 'Data/ArticleLevel-RegData-ALLSA_Xc_1_NData_655386.dta'


```

#### Read Input File
```{r echo=FALSE, warning=FALSE, message=FALSE}
# df_article = read.csv(article_file, stringsAsFactors = FALSE)
# print(paste0("# of rows: ", nrow(df_article)))
# head(df_article)

df_article = read_dta(article_file)
print(paste0("# of rows: ", nrow(df_article)))
head(df_article)

```

#### Filters
###### Filter Year [1970-2018]
###### Filter Kp >= 2 and Wp >= 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
# df_article = df_article %>% filter(Yp >= 1970 & Yp <= 2018) %>% filter(Kp >= 2) %>% filter(nMeSHMain >= 2)
df_article = df_article %>% filter(Yp >= 1970)
df_article = df_article %>% filter(Yp <= 2018)
df_article = df_article %>% filter(Kp >= 2)
df_article = df_article %>% filter(nMeSHMain >= 2)
df_article = df_article %>% filter(IRegionRefinedp > 0 & IRegionRefinedp < 7)
print(paste0("# of rows: ", nrow(df_article)))
head(df_article)
```


## Convert Data Types
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article$eidsp = as.factor(df_article$eidsp)
df_article$Yp = as.integer(df_article$Yp)
df_article$Kp = as.integer(df_article$Kp)
df_article$MeanZJp = as.double(df_article$MeanZJp)
df_article$XSAp = as.factor(df_article$XSAp)
df_article$XCIPp = as.factor(df_article$XCIPp)
df_article$NRegp = as.integer(df_article$NRegp)
df_article$NSAp = as.integer(df_article$NSAp)
df_article$NCIPp = as.integer(df_article$NCIPp)
df_article$nMeSHMain = as.integer(df_article$nMeSHMain)
df_article$IRegionRefinedp = as.factor(df_article$IRegionRefinedp)
df_article$Regionp = as.factor(df_article$Regionp)
```



## Model 1 - for X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model1 <- glm(XSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp , data = df_article, family=binomial(link='logit'))
summary(model1)

## For R-squared value
nagelkerke(model1)

## odds ratio
output = odds.ratio(model1)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 2 - for X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model2 <- glm(XCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp , data = df_article, family=binomial(link='logit'))
summary(model2)

## For R-squared value
nagelkerke(model2)

## odds ratio
output = odds.ratio(model2)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 3 - for X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTXSACIPp!=1) 

options(scipen=2)
model3 <- glm(XSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp , data = df_article_SACIP, family=binomial(link='logit'))
summary(model3)

## For R-squared value
nagelkerke(model3)

## odds ratio
output = odds.ratio(model3)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

# Shifts after Funding

## Model 4 - for X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model4 <- glm(XSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model4)
# 
# ## For R-squared value
nagelkerke(model4)
# 
# ## odds ratio
output = odds.ratio(model4)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


## Model 5 - for X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model5 <- glm(XCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model5)
# 
# ## For R-squared value
nagelkerke(model5)
# 
# ## odds ratio
output = odds.ratio(model5)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 6 - for X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTXSACIPp!=1) 

options(scipen=2)
model6 <- glm(XSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
              , data = df_article_SACIP, family=binomial(link='logit'))
summary(model6)

## For R-squared value
nagelkerke(model6)

## odds ratio
output = odds.ratio(model6)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


# Distant
## Model 1 - for X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model1 <- glm(NEUROLONGXSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp , data = df_article, family=binomial(link='logit'))
summary(model1)

## For R-squared value
nagelkerke(model1)

## odds ratio
output = odds.ratio(model1)
output = apply(output, 2, formatC, format="f", digits=4)
output

```

## Model 2 - for Distant X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model2 <- glm(NEUROLONGXCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp , data = df_article, family=binomial(link='logit'))
summary(model2)

## For R-squared value
nagelkerke(model2)

## odds ratio
output = odds.ratio(model2)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 3 - for Distant X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTNEUROLONGXSACIPp!=1) 

options(scipen=2)
model3 <- glm(NEUROLONGXSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp , data = df_article_SACIP, family=binomial(link='logit'))
summary(model3)

## For R-squared value
nagelkerke(model3)

## odds ratio
output = odds.ratio(model3)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


# Shifts after Funding - Distant

## Model 4 - for Distant X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model4 <- glm(NEUROLONGXSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model4)
# 
# ## For R-squared value
nagelkerke(model4)
# 
# ## odds ratio
output = odds.ratio(model4)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


## Model 5 - for Distant  X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model5 <- glm(NEUROLONGXCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model5)
# 
# ## For R-squared value
nagelkerke(model5)
# 
# ## odds ratio
output = odds.ratio(model5)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 6 - for Distant  X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTNEUROLONGXSACIPp!=1) 

options(scipen=2)
model6 <- glm(NEUROLONGXSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
              , data = df_article_SACIP, family=binomial(link='logit'))
summary(model6)

## For R-squared value
nagelkerke(model6)

## odds ratio
output = odds.ratio(model6)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


# Neighboring
## Model 1 - for Neighboring X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model1 <- glm(NEUROSHORTXSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp , data = df_article, family=binomial(link='logit'))
summary(model1)

## For R-squared value
nagelkerke(model1)

## odds ratio
output = odds.ratio(model1)
output = apply(output, 2, formatC, format="f", digits=4)
output

```

## Model 2 - for Neighboring X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
options(scipen=2)
model2 <- glm(NEUROSHORTXCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp , data = df_article, family=binomial(link='logit'))
summary(model2)

## For R-squared value
nagelkerke(model2)

## odds ratio
output = odds.ratio(model2)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 3 - for Neighboring X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTNEUROSHORTXSACIPp!=1) 

options(scipen=2)
model3 <- glm(NEUROSHORTXSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp , data = df_article_SACIP, family=binomial(link='logit'))
summary(model3)

## For R-squared value
nagelkerke(model3)

## odds ratio
output = odds.ratio(model3)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


# Shifts after Funding - Neighboring

## Model 4 - for Neighboring X_SA
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model4 <- glm(NEUROSHORTXSAp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NCIPp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model4)
# 
# ## For R-squared value
nagelkerke(model4)
# 
# ## odds ratio
output = odds.ratio(model4)
output = apply(output, 2, formatC, format="f", digits=4)
output


```


## Model 5 - for Neighboring  X_CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}


# options(scipen=2)
model5 <- glm(NEUROSHORTXCIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + NSAp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
                , data = df_article, family=binomial(link='logit'))
summary(model5)
# 
# ## For R-squared value
nagelkerke(model5)
# 
# ## odds ratio
output = odds.ratio(model5)
output = apply(output, 2, formatC, format="f", digits=4)
output


```

## Model 6 - for Neighboring  X_SA&CIP
```{r echo=FALSE, warning=FALSE, message=FALSE}
df_article_SACIP = df_article %>% filter(NOTNEUROSHORTXSACIPp!=1) 

options(scipen=2)
model6 <- glm(NEUROSHORTXSACIPp ~ Yp + MeanZJp + logKp + logMajorMeSHp + NRegp + IYBRAINPROJECTp + Regionp + (Regionp * factor(IYBRAINPROJECTp))
              , data = df_article_SACIP, family=binomial(link='logit'))
summary(model6)

## For R-squared value
nagelkerke(model6)

## odds ratio
output = odds.ratio(model6)
output = apply(output, 2, formatC, format="f", digits=4)
output


```
